# Substantial pain (50% reduction)


```{r eval=FALSE}
subgroup_type %>% 
  filter(outcome == "pain_sub",
         # timepoint == "post_int",
         type == "ad"
         )

```


```{r }
this_key_row <- 
subgroup_type %>% 
  filter(
    outcome == "pain_sub",
    timepoint == "post_int",
    type == "ad"
  )

```


```{r eval=FALSE}
nma_pain <- 
  pres_nma(this_key_row)

write_pres_nma(nma_pain, this_key_row)

```

```{r}
nma_pain_sub <- read_rds("data/pres/subgroup_type_pain_sub_ad_post_int_.rds")

```

```{r}
nma_pain_sub_plot <- make_forest(nma_pain_sub, this_key_row) 

```

***

```{r}
nma_pain_sub_plot + 
  facet_grid(class ~ ., scales = "free", space = "free") + 
  coord_cartesian(xlim = c(-1,7.5))

```


***

```{r}
make_forest(nma_pain_sub, this_key_row, this_class = "snri") +
  facet_grid(class ~ ., scales = "free", space = "free") 

```

***

```{r}
make_forest(nma_pain_sub, this_key_row, this_class = "tca") 

```


## Do NMA results for SNRI differ from pairwise comparisons?

```{r }
this_pw <- 
pw_results %>% 
  filter(subgroup == "subgroup_class",
         outcome == "pain_sub",
         class == "snri"
         ) %>% 
  arrange(desc(n_studies)) 

  
this_pw %>%   
  select(int_1, int_2, n_studies) %>% 
  gt() %>% 
  cols_label(
    int_1 = "Control",
    int_2 = "Treatment",
    n_studies = "Studies"
  ) %>% 
  tab_header("Possible meta-analtyic comparisons for SNRI")
  


```

***

```{r}
this_pw[1,]$pw_forest_file %>% read_rds() +
  coord_cartesian(xlim = c(0, 6))

```

*** 
```{r}
this_pw[2,]$pw_forest_file %>% read_rds() 

```

***

```{r}
this_pw[3,]$pw_forest_file %>% read_rds()

```


***

```{r}
this_pw[4,]$pw_forest_file %>% read_rds()

```


##  Substantial pain | Do the results differ for fibromyalgia?

```{r eval=FALSE}
subgroup_con %>% 
  filter(outcome == "pain_sub",
         ) %>% 
  select(outcome, timepoint, condition, participants_int, n_studies, type) %>% 
  arrange(desc(participants_int), desc(n_studies))    

```


```{r }
this_pw <- 
pw_results %>% 
  filter(
    outcome == "pain_sub",
    subgroup == "subgroup_con"
  ) %>% 
  arrange(desc(participants), desc(n_studies))

this_tab <- 
this_pw %>% 
  select(int_1, int_2, condition, participants, n_studies) %>% 
  gt() %>% 
  cols_label(
    int_1 = "Control",
    int_2 = "Treatment",
    n_studies = "Studies",
    condition = "Condition"
  ) %>% 
  tab_header("Duloxetine and milnacipran pairwise for specific conditions")


```


***

```{r }
this_key_row <- 
subgroup_con %>% 
  filter(
    outcome == "pain_sub",
    timepoint == "post_int",
    type == "ad",
    condition == "fibromyalgia"
  )

```


```{r eval=FALSE}
nma_pain_fibro <- 
  pres_nma(this_key_row)

write_pres_nma(nma_pain_fibro, this_key_row)

```

```{r}
nma_pain_fibro <- read_rds("/home/cantabile/Documents/gh-repos/adpain/data/pres/subgroup_con_pain_sub_ad_post_int_fibromyalgia_.rds")

```

```{r}
nma_pain_fibro_plot <- make_forest(nma_pain_fibro, this_key_row) 

```


```{r}
nma_pain_fibro_plot + 
  facet_grid(class ~ ., scales = "free", space = "free")

```

***
```{r}
this_pw %>% 
  filter(condition == "fibromyalgia") %>% 
  slice(1) %>% 
  pull(pw_forest_file) %>% 
  read_rds()
  
```

***
```{r}
this_pw %>% 
  filter(condition == "fibromyalgia") %>% 
  slice(2) %>% 
  pull(pw_forest_file) %>% 
  read_rds()
  
```

***
```{r}
this_pw %>% 
  filter(condition == "fibromyalgia") %>% 
  slice(3) %>% 
  pull(pw_forest_file) %>% 
  read_rds()
  
```

##  Substantial pain | Do the results differ for musculoskeletal?


***


```{r }
this_key_row <- 
subgroup_con %>% 
  filter(
    outcome == "pain_sub",
    timepoint == "post_int",
    type == "ad",
    condition == "musculoskeletal"
  )

```


```{r eval=FALSE}
nma_pain_muscu <- 
  pres_nma(this_key_row)

write_pres_nma(nma_pain_muscu, this_key_row)

```

```{r}
nma_pain_muscu <- read_rds("/home/cantabile/Documents/gh-repos/adpain/data/pres/subgroup_con_pain_sub_ad_post_int_musculoskeletal_.rds")

```

```{r}
nma_pain_muscu_plot <- make_forest(nma_pain_muscu, this_key_row) 

```


```{r}
nma_pain_muscu_plot + 
  facet_grid(class ~ ., scales = "free", space = "free")

```




***
```{r}
this_pw %>% 
  filter(str_detect(condition, "musc")) %>% 
  pull(pw_forest_file) %>% 
  read_rds() +
  coord_cartesian(xlim = c(0, 10))
  
```


## Substantial pain | Do the results differ for neuropathic?

***

```{r }
this_key_row <- 
subgroup_con %>% 
  filter(
    outcome == "pain_sub",
    timepoint == "post_int",
    type == "ad",
    condition == "neuropathic"
  )

```


```{r eval=FALSE}
nma_pain_neuro <- 
  pres_nma(this_key_row)

write_pres_nma(nma_pain_neuro, this_key_row)

```

```{r}
nma_pain_neuro <- read_rds("/home/cantabile/Documents/gh-repos/adpain/data/pres/subgroup_con_pain_sub_ad_post_int_neuropathic_.rds")

```

```{r}
nma_pain_neuro_plot <- make_forest(nma_pain_neuro, this_key_row) 

```


```{r}
nma_pain_neuro_plot + 
  facet_grid(class ~ ., scales = "free", space = "free") +
  coord_cartesian(xlim = c(-2, 4))

```

***
```{r}
this_pw %>% 
  filter(str_detect(condition, "neuro")) %>% 
  slice(1) %>% 
  pull(pw_forest_file) %>% 
  read_rds()
  
```



## Is there a difference in results for dose? | Substantial pain


```{r}
this_pw <- 
pw_results %>% 
  filter(outcome == "pain_sub",
         subgroup == "subgroup_dose"
         )

this_pw %>% 
  select(timepoint_label, comp, dose, n_studies, participants, int_2) %>% 
  arrange(comp, dose) %>%
  rename_with(str_to_sentence, everything()) %>% 
  gt(groupname_col = "Int_2") %>% 
  tab_header("Pairwise comparisons of substantial pain by dose") %>% 
  cols_label(
    N_studies = "Studies",
    Comp = "Comparison"
  ) %>% 
  tab_options(row_group.background.color = hpp_pal(1)
    
  )
  
```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "dulox"), dose == "high") %>% 
  pull(pw_forest_file) %>% 
  read_rds() +
  coord_cartesian(xlim = c(0,5))

```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "dulox"), dose == "standard") %>% 
  pull(pw_forest_file) %>% 
  read_rds() +
  coord_cartesian(xlim = c(0,5))

```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "dulox"), dose == "low") %>% 
  pull(pw_forest_file) %>% 
  read_rds() +
  coord_cartesian(xlim = c(0,5))

```

## Does desvenlafaxine show the same attributes?

Effective across doses? Results agree across doses?

```{r}
this_pw %>%
  filter(str_detect(int_2, "desv")) %>% 
  select(timepoint_label, comp, dose, n_studies, participants, int_2) %>% 
  arrange(comp, dose) %>%
  rename_with(str_to_sentence, everything()) %>% 
  gt(groupname_col = "Int_2") %>% 
  tab_header("Pairwise comparisons of substantial pain by dose") %>% 
  cols_label(
    N_studies = "Studies",
    Comp = "Comparison"
  ) %>% 
  tab_options(row_group.background.color = hpp_pal(1)
    
  )
  
```

***


```{r}
this_pw %>% 
  filter(str_detect(int_2, "desv"), dose == "high") %>% 
  pull(pw_forest_file) %>% 
  read_rds()

```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "desv"), dose == "standard") %>% 
  pull(pw_forest_file) %>% 
  read_rds() 

```

## Do results agree for milnacipran?

```{r}
this_pw %>%
  filter(str_detect(int_2, "miln")) %>% 
  select(timepoint_label, comp, dose, n_studies, participants, int_2) %>% 
  arrange(comp, dose) %>%
  rename_with(str_to_sentence, everything()) %>% 
  gt(groupname_col = "Int_2") %>% 
  tab_header("Pairwise comparisons of substantial pain by dose") %>% 
  cols_label(
    N_studies = "Studies",
    Comp = "Comparison"
  ) %>% 
  tab_options(row_group.background.color = hpp_pal(1)
    
  )

```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "miln"), dose == "standard") %>% 
  pull(pw_forest_file) %>% 
  read_rds()

```

***

```{r}
this_pw %>% 
  filter(str_detect(int_2, "miln"), dose != "standard") %>% 
  pull(pw_forest_file) %>% 
  read_rds() 

```

***

#### A final look at overall results for substantial pain

***

```{r}
nma_pain_sub_plot + 
  facet_grid(class ~ ., scales = "free", space = "free") + 
  coord_cartesian(xlim = c(-1,7.5))

```


