# Pipeline

## Check figure sizing

```{r results="asis"}
 glue("<img src=\"images/dev/forest.png\" style = 'width:200%;' />") %>%
    cat()
```


## Joining together Covidence export with Hollie's extractions


```{r, eval=FALSE}
tar_read(w_study_report)


```

    
    
## Labelling protocol for Covidence

```{r load w_obs, eval=FALSE}
tar_load(w_obs) 

  
```

### Labels not specific to outcome

#### Condition

```{r output levels of w_obs, eval=FALSE}
w_obs %>% 
  summarise(
    condition_general = unique(condition_general) 
  ) 

```


#### Timepoint or change score

```{r, eval=FALSE}
w_obs %>% 
  count(timepoint)

```

##### Unmatched timepoints

```{r, eval=FALSE}
tar_read(w_obs_timepoint) %>% 
  filter(timepoint == "unmatched") %>% 
  select(study, arm, covidence_desc)
```



### Labels specific to outcome

#### Scales

```{r outcome levels, eval=FALSE}
w_obs %>% 
  group_by(outcome) %>% 
  count(scale) %>% 
  gt(
    groupname_col = "outcome"
  )

```

## Checks

Check that key points in pipeline have the expected number of joins and meets.

```{r, eval=FALSE}
tar_load(w_covidence)
tar_load(w_obs_long_final)
tar_load(w_cov)
tar_load(w_obs)
```

```{r, eval=FALSE}
targets <- 
list(
  w_covidence = w_covidence,
  w_cov = w_cov,
  w_obs_long_final = w_obs_long_final
) 

targets %>% 
  map_df(.f = function(df) {
    tibble(
    nrow = nrow(df),
    studies = df$study %>% unique() %>% length(),
    arms = df$arm %>% unique() %>% length()
    )
  }) %>% 
  mutate(
    target = names(targets)
  ) %>% 
  select(target, everything()) %>% 
  gt()


```

## subgroups

### condition

```{r, eval=FALSE}

```


## Number of arms per study per timepoint

```{r, eval=FALSE}
w_obs %>% 
  group_by(outcome, timepoint) %>% 
  count(study)

```
