# Documentation

## Calculations for missing observations

Where possible required statistics calculated from reported statistics.

Confidence intervals assumed to have $\alpha = 0.05$; i.e., 95% confidence intervals assumed.  

If medians and interquartile ranges were reported, then means and standard deviations were estimated using an implmentation [@gray_2021] of [@wan_2014]'s method.

Symbol | Statistic
-|-
$n$ | Sample size
$r$ | Rate
$s$ | Standard deviation
$\text{se}$ | Standard error
$U$ | Upper confidence interval
$L$ | Lower confidence interval
$\alpha$ | Confidence level (0.05 assumed)
$\overline x$ | Mean
$\Phi$ | Standard normal cumulative density function
$M$ | Median

Missing | Reported | Calculation | Code
-|-|-----------|---------------------------
$n$ | $\%, r$ | $n = r / \%$ | `n = round(r / r_percent)`
$r$ | $\%, n$ | $r = \% \times n$ | `\r = r_percent * n` 
$s$, $\text{se}$ | $\overline x, n, U$ | $s = \sqrt{n}(U - \overline x)/\Phi^{-1}(1 - \alpha/2)$ | `sd = sqrt(n) * (ci_upper - mean) / qnorm(1 - 0.05/2)`
$s$, $\text{se}$ | $\overline x, n, L$ | $s = \sqrt{n}(\overline x - L)/\Phi^{-1}(1 - \alpha/2)$ | `sd = sqrt(n) * (mean - ci_lower) / qnorm(1 - 0.05/2)`
$\overline x$ | $M, U, L$ | $\overline x \approx (L + M + U)/3$ [@wan_2014] | `mean = varameta::wan_mean_C3(q_1 = iqr_lower, m = median, q_3 = iqr_higher)` [@gray_2021]
$\text{se}$ | $M, U, L, n$ | $\text{se} = (U - L)/(2\sqrt{n}\Phi^{-1}((0.75n-0.125)/(n+0.25)))$ [@wan_2014] | `se = varameta::wan_se_C3(q_1 = iqr_lower, m = median, q_3 = iqr_higher, n = n)` [@gray_2021]
$s$ | $\text{se}, n$ | $s = \text{se} \times \sqrt{n}$ | `sd = se * sqrt(n)`
$\text{se}$ | $s, n$ | $\text{se} = s / \sqrt{n}$ | `se = sd / sqrt(n)`

## Direction of improvement

The assumed direction of improvement for each outcome is encoded in `direction_of_improvement` (see table below). For standardised mean difference `smd` outcomes, where the scale reported was opposite to the assumed direction, the mean was set to `-mean`.

```{r dir, fig.cap="Assumed direction of improvement for each outcome."}
obs_dat %>% 
  filter(!str_detect(outcome, "_adverse|adverse_"), 
         !is.na(outcome)) %>% 
  count(outcome, direction_of_improvement, scale_dir, model_type)  %>% 
  gt()


```

## Are the converted values similar to the raw values? 

In the below table, ... for the same scale and outcome?

```{r pw-nma, fig.cap="For the same outcome, and scale, do the converted values broadly agree with the raw values?"}


```



## Number of studies extracted: `r w_obs_outcome %>% pull(study_id) %>% unique() %>% length()`

## Excluded observations: `r nrow(obs_excluded)` from `r obs_excluded %>% pull(study_id) %>% unique() %>% length()` studies

For odds-ratio the rate and sample size are required for NMA, and for standardised mean difference, the mean, standard deviation, and sample size are required. Where there are missing reported statistics, and required statistics cannot be calculated from what is reported, the observations are excluded from the models. 


```{r}
obs_excluded %>% 
  count(study_id, timepoint, change_score) %>% 
  gt() %>% 
  tab_header("Number of observations (study/arm statistics) excluded by study")
```


```{r}
obs_excluded %>% 
  select(exclusion_reason, gs_row, outcome, study_id, intervention, timepoint, mean:change_score) %>% 
  gt(groupname_col = "study_id",
     rowname_col = "exclusion_reason"
     ) %>% 
  tab_header("Observations currently excluded") %>% 
  tab_options(
    table.font.size = 12,
        row_group.background.color = hpp_pal(1)

  )

```


## Random sample checked

```{r}

checked_obs <- list(
  checked = sum(!is.na(w_obs_outcome$date_checked)),
  total_obs = nrow(w_obs_outcome)
)

checked_obs$prop <- checked_obs$checked/checked_obs$total_obs

checked_obs %>% 
  as_tibble() %>% 
  gt() %>% 
  cols_label(
    checked = "Observations checked (statistics reported for one arm of one study)",
    total_obs = "Total observations extracted",
    prop = "Proportion of observations checked"
  ) %>% 
  tab_header(
    title = "Charles' progress checking Covidence records against dataset"
  )

```



