---
title: "Antidepressants for pain management in adults with chronic pain"
description: |
  Network meta-analysis results
site: bookdown::bookdown_site
bibliography: references.bib
---

# Overview

Placeholder


## Observations included
## Summary by condition
## Summary by class
## Summmary by intervention
## Comparisons

<!--chapter:end:index.Rmd-->


# Pain intensity (continuous measure)

Placeholder


## Summary of findings: post-intervention 
### PICO
## Antidepressant NMA
### Direct evidence
## Pain intensity & SNRI
## Direct evidence for SNRI in pain intensity
## SSRI & pain intensity
## No direct evidence for SSRI in pain intensity
## Pain intensity and TCA
## Pain intensity | Only direct evidence for amitriptyline

<!--chapter:end:1-pain_int.Rmd-->


# Substantial pain (50% reduction)

Placeholder


## Antidepressant
### Antidepressants: direct evidence
## Direct evidence and condition
## Non-antidepressant pharmacological
## from pres
## Do NMA results for SNRI differ from pairwise comparisons?
##  Substantial pain | Do the results differ for fibromyalgia?
##  Substantial pain | Do the results differ for musculoskeletal?
## Substantial pain | Do the results differ for neuropathic?
## Is there a difference in results for dose? | Substantial pain
## Does desvenlafaxine show the same attributes?
## Do results agree for milnacipran?
#### A final look at overall results for substantial pain

<!--chapter:end:2-pain_sub.Rmd-->

# Moderate pain (30% reduction)


<!--chapter:end:3-pain_mod.Rmd-->


# Mood

Placeholder


## Antidepressant 
### NMA: post-intervention 
### Antidepressant NMA: change score
### Direct evidence
## SNRI and mood
### First we'll look at duloxetine and then the other results

<!--chapter:end:4-mood.Rmd-->

# Physical function

```{r results='asis', warning=FALSE}
makechapter("physical")  #<- sink
```


<!--chapter:end:5-physical.Rmd-->

# Sleep


<!--chapter:end:6-sleep.Rmd-->

# Quality of life



<!--chapter:end:7-qol.Rmd-->


# Adverse events

Placeholder


## Adverse events
### Direct evidence for adverse events
## Serious adverse events
### Duloxetine
## Dropout due to adverse events

<!--chapter:end:8-adverse.Rmd-->

# Withdrawal


<!--chapter:end:9-withdrawal.Rmd-->

# Duloxetine



<!--chapter:end:91-duloxetine.Rmd-->


# Documentation

Placeholder


## ACR
## Calculations for missing observations
## Direction of improvement
## Are the converted values similar to the raw values? 
## Number of studies extracted: `r w_obs_outcome %>% pull(study_id) %>% unique() %>% length()`
## Excluded observations: `r nrow(obs_excluded)` from `r obs_excluded %>% pull(study_id) %>% unique() %>% length()` studies
## Random sample checked
## Getting data
## Tasks
### Placebo vs duloxetine
### Getting NMA data

<!--chapter:end:99-documentation.Rmd-->

---
title: "Summary of findings development"
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1cm"
output: 
  html_document:
    toc: true
    toc_float: true
    fig_align: center
  # pdf_document
  # pdf_document:
  #   extra_dependencies: "subfig"
  # ioslides_presentation:
  #   widescreen: true

---

```{r eval=FALSE, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  echo = FALSE
  )


library(targets)
library(kableExtra)
library(adpain)
library(multinma)
library(tidyverse)
tar_load(rob)
tar_load(sof_acr)
tar_load(timepoint_key)
tar_load(type_key)


conflicted::conflict_prefer("filter", "dplyr")



```

```{r eval=FALSE}
sof_output <- function(this_mod) {
  
  # results table
  sof_results_dat(this_mod) %>%
    left_join(rob) %>% 
    mutate(high_risk_p = round(high_risk_p, 2)) %>% 
    mutate(intervention = str_to_sentence(intervention)) %>% 
    select(intervention, 
           # type,
           # timepoint,
           RCT = tab_rct,
           participants,
           rel = tab_rel, 
           high_risk_p,
           rank = tab_rank) %>% 
    kable(
      col.names = c(
        "Intervention",
        # "Type",
        # "Timepoint",
        "RCT",
        "Participants",
        "Relative effect (2)",
        "p[ROB] (3)",
        "Rank (2)"
      )
    ) %>% 
    kable_styling() %>% 
    add_footnote(
      c("RCT := Number of randomised control trials", 
        "Mean estimate with 95 per cent credible interval",
        "p[ROB] := Proportion of high-bias observations"
        ), 
      notation = "number"
    ) %>% 
    column_spec(4, width = "4cm") %>% 
    column_spec(6, width = "3cm")

  }

sof_output_acr <- function(this_mod, acr = 0.31) {

  results <- sof_results_dat(this_mod) %>% 
    left_join(rob) %>% 
    mutate(
      high_risk_p = high_risk_p %>% round(2)
    )
  
  
  acr_dat <-
   results %>% 
    sof_nnt(acr) %>%
    select(intervention, nf_1000, nnt)
  
  results %>% 
    left_join(acr_dat) %>%
    mutate(nnt = glue("{nnt} of 1000")) %>% 
    arrange(nnt) %>% 
    select(intervention,
           # type, 
           # timepoint,
           RCT = tab_rct,
           participants,
           # nf_1000,
           NNTH = nnt,
           rel = tab_rel, 
           high_risk_p,
           rank = tab_rank
           ) %>% 
    mutate(intervention = str_to_sentence(intervention)) %>% 
    kable(
            col.names = c(
        "Intervention",
        # "Type",
        # "Timepoint",
        "RCT (1)",
        "Participants",
        "NNTH (3)",
        "Relative effect (2)",
        "p[ROB] (4)",
        "Rank (2)"
      )

    ) %>% 
    kable_styling() %>% 
    add_footnote(
      c("RCT := Number of randomised control trials", 
        "Mean estimate with 95 per cent credible interval",
        "NNTH: Number needed to treat to harm",
        "p[ROB] := Proportion of high-bias observations"
        ), 
      notation = "number"
    ) %>% 
    column_spec(5, width = "4cm") %>% 
    column_spec(7, width = "3cm")
}

sof_output_styling <- function(so) {

}

sof_pico <- function(this_mod) {
  this_mod$network$agd_arm %>% 
    left_join(timepoint_key %>% select(timepoint, timepoint_label)) %>% 
    left_join(type_key %>% select(type, type_label)) %>% 
    summarise(
      outcome = unique(outcome_label),
      timepoint = unique(timepoint_label),
      type = unique(type_label) %>% 
        paste(collapse = ";") %>% str_remove(";*placebo;*"),
      participants = sum(n),
      studies = n_distinct(.study),
      model = unique(model_text)
    ) %>% 
    mutate(
      population = "adults with chronic pain",
      comparator = "placebo"
    ) %>% 
    select(
      population, outcome, type, timepoint, everything(), comparator 
    ) %>% 
    t() %>% 
    as_data_frame(rownames = "descriptor") %>% 
    rename(
      details = V1
    ) %>% 
    mutate(across(everything(), str_to_sentence)) %>% 
    kable(col.names = NULL) %>% 
    kable_styling()
    
}

```




```{r eval=FALSE}

sof_acr %>% 
  left_join(outcome_key) %>% 
  mutate(acr = round(acr, 2)) %>% 
  select(Outcome = outcome_label, ACR = acr) %>% 
  kable() %>% 
  kable_styling(full_width = F)

```


## Pain intensity 

### Change score

```{r}

this_mod <- 
  read_rds("exports/pain_int/nma-cs.rds")

sof_pico(this_mod)

this_mod$network %>% plot()

sof_output(this_mod) 


```


### Post-intervention

```{r}

this_mod <- read_rds("exports/pain_int/nma-pi.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 


```


## Adverse 

```{r }

this_mod <- read_rds("exports/adverse/nma-adverse.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
this_acr <- 
  sof_acr %>% 
  filter(outcome == "adverse") %>% 
  pull(acr)
sof_output_acr(this_mod, this_acr) 


```


## Mood

### Change score

```{r }

this_mod <- read_rds("exports/mood/nma-mod-cs.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```


### Post-intervention

```{r }

this_mod <- read_rds("exports/mood/nma-mood.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 


```

## Serious adverse


```{r }

this_mod <- read_rds("exports/adverse/nma-serious.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
this_acr <- 
  sof_acr %>% 
  filter(outcome == "adverse") %>% 
  pull(acr)
sof_output_acr(this_mod, this_acr) 


```


## Dropout due to adverse events


```{r }

this_mod <- read_rds("exports/adverse/nma-dropout.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
this_acr <- 
  sof_acr %>% 
  filter(outcome == "adverse_dropout") %>% 
  pull(acr)
sof_output_acr(this_mod, this_acr) 


```


## Substantial pain

```{r }

this_mod <- read_rds("exports/pain_sub/nma-sub.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output_acr(this_mod, outcome_acr("pain_sub")) 


```


## Moderate pain

```{r}

this_mod <- read_rds("exports/pain_mod/nma-mod.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
this_acr <- 
  sof_acr %>% 
  filter(outcome == "pain_mod") %>% 
  pull(acr)

sof_output_acr(this_mod,this_acr) 



```


## Sleep


### Change score

```{r }


this_mod <- read_rds("exports/sleep/nma-mod-cs.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 
```


### Post intervention

```{r }

this_mod <- read_rds("exports/sleep/nma-mod.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```

## Withdrawal

```{r}
this_mod <- read_rds("exports/withdrawal/nma-mod.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
this_acr <- 
  sof_acr %>% 
  filter(outcome == "withdrawal") %>% 
  pull(acr)
sof_output_acr(this_mod, this_acr) 

```

## Quality of life


### Change score

```{r}
this_mod <- read_rds("exports/qol/nma-mod-cs.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```

### Post intervention

```{r}
this_mod <- read_rds("exports/qol/nma-mod.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```


## Physical functioning

### Change score

```{r}
this_mod <- read_rds("exports/physical/nma-mod-cs.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```

### Post intervention

```{r}
this_mod <- read_rds("exports/physical/nma-mod.rds")
sof_pico(this_mod)
this_mod$network %>% plot()
sof_output(this_mod) 

```

<!--chapter:end:sof.Rmd-->

