---
title: "Antidepressants for pain management in adults with chronic pain"
description: |
  Network meta-analysis results
site: bookdown::bookdown_site
bibliography: references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.width = 10,
                      fig.height = 8,
                      eval=TRUE,
                      error = TRUE,
                      warnings = FALSE, 
                      message = FALSE)

knitr::opts_knit$set(root.dir = "../")

suppressPackageStartupMessages({
  library(tidyverse)
  library(multinma)
  library(targets)
  library(assertthat)
  library(glue)
  library(gt)
  library(janitor)
  library(broom)
  library(adpain)
})

source("preamble.R")

```

# Overview

## Subgroups

### Subgroups by timepoint

We were deliberately broad in the protocol as it wasn't clear how conventional, or feasible, it was to study participants over multiple timepoints. 

In addition, some studies reported change scores, as opposed to post-intervention outcomes. We are currently doing some reading on how to combine these statistics, but are currently dividing change score and post-intervention analyses into separate subgroups. 


```{r}
tps <-
timepoint_key %>% 
  drop_na() %>% 
  pull(timepoint_label) %>% 
  paste(collapse = "; ")

```

We collected data at timepoints `r tps`. However, some studies were excluded due to not reporting the statistics required to include in meta-analysis (e.g., sample size). When we look at the timepoints for each outcome, we see that post-intervention is the only timepoint routinely reported:

```{r}
mod_dat %>% 
  group_by(outcome, timepoint) %>% 
  summarise(
    n_studies = n_distinct(study),
    n_participants = sum(n)
  ) %>% 
  gt() %>% 
  hpp_tab()
  
```

### Interventions

- more duloxetine than any others

